Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-16 paper.tex
tikz is fun
Section 5 draft

@@

\section{Scalable Output Approximation}%
The main objective of this experience report is to investigate whether we can
have a scalable symbolic execution engine as it is the underlying technique for
static output approximation in previous work
\cite{Nguyen:2011:AFH:2190078.2190142,Nguyen:2014:BCG:2635868.2635928,Nguyen:2015:CPS:2786805.2786872,Nguyen:2015:VIS:2819009.2819140}.
Our vision is a practical symbolic execution, i.e., it computes an accurate approximation for large and modern PHP systems with reasonable time and space consumption.

@@

% Callback candidate description
\begin{figure}[t!]
	%\centering
	\includegraphics[scale=0.55]{images-paper/callgraph_cases}
    \caption{Callgraph analysis: The bottom nodes represent functions
    containing missed output candidates, the top nodes depict entry points to
    them.}
    \label{fig:callgraph} 
\end{figure}

@@

\section{Lessons Learned}
%\textcolor{blue}{\Blindtext}

\section{Related Work} \label{sec:related_work}
\cite{Hills:2013:ESP:2483760.2483786}
\cite{wassermann2007sound,minamide2005static}
%\textcolor{blue}{\blindtext\blindtext}

>>>>

\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

@@

\section{Scalable Output Approximation} \label{sec:3}
The main objective of this experience report is to investigate whether we can
have a scalable symbolic execution engine as it is the underlying technique for
static output approximation in previous work
\cite{Nguyen:2011:AFH:2190078.2190142,Nguyen:2014:BCG:2635868.2635928,Nguyen:2015:CPS:2786805.2786872,Nguyen:2015:VIS:2819009.2819140}.
Our vision is a practical symbolic execution, i.e., it computes an accurate approximation for large and modern PHP systems with reasonable time and space consumption.

@@

% Callback candidate description
\begin{figure}
	%\centering
	%\includegraphics[scale=0.55]{images-paper/callgraph_cases}
    \input{new_diagrams/callback_classification}
    \caption{Callgraph analysis: The bottom nodes represent functions
    containing missed output candidates, the top nodes depict entry points to
    them.}
    \label{fig:callgraph} 
\end{figure}

@@

\section{Lessons Learned}
In this section we summarize the insights gained from our observations during
the implementation as well as the from the results obtained by our experimental
evaluation.

\paragraph{Features are problematic, but prevalently used.}
From out observations with \sf{WordPress} in Section \ref{sec:3} we learn that
dynamic language features, in particular include expressions and indirect function
calls, in combination with symbolic values cannot be evaluated accurately since
concrete values are required. For our observations we were able to explain most
of the missed output candidates with indirect function calls. For include
expressions we are indeed able to resolve most expressions successfully, yet we
do not distinguish between static and dynamic includes in this case study as
this would exceed the scope of our paper. However, we believe it is plausible
to assume that defective include expressions can cause a cascade of missing
files and subsequent includes.
Throughout the experiment we have seen that dynamic features, are prevalent for
modern PHP systems as they serve a genuine purpose in the programming language.
Nevertheless their usage in situations when combined with assumed symbolic
values restricts symbolic execution and any tool leveraging results obtained
from that.

\paragraph{Bypassing conceptual limitations.}
Symbolic execution is used to approximate client page output since it allows to
unfold the staged nature of dynamic web applications. Aside from conceptual
limitations in the systems studied, limitations can be addressed. To use
approaches incorporating symbolic execution with dynamic web applications in
the long run, more concrete dummy information, similar to test oracles, needs
to be provided to decrease the number of assumed symbolic inputs and avoid
dynamic features being confronted with symbolic values.Also, if the usage of
tools using static output approximation with symbolic execution is intended,
avoiding dynamic features that are prone to be inaccurately executed for
symbolic execution  may be an adjustment strategy to program in an analyzable
way.

\paragraph{Practical tools require practical evaluation.}
Last, we want to address the limited informative value of analyses and tools
presented in previous work \cite{minamide2005static,wassermann2007sound,Nguyen:2015:VIS:2819009.2819140,Nguyen:2015:CPS:2786805.2786872,Nguyen:2014:BCG:2635868.2635928,Nguyen:2011:AFH:2190078.2190142}
 where only small PHP systems  have been studied. These papers introduce
 techniques for static output approximation of PHP web applications [X, Y] or
 propose tools based on respective approximations [Z, Wassermann]. As these
 approaches address practical use cases, they require a more and further
 comprehensive evaluation in order to  better understand possible limitations
 and assess their practicality, in particular for large-scale systems.

\paragraph{The road so far.}
For this paper, the extension of the symbolic execution Symex [Hung] support
for object-oriented programming was not the main goal, yet necessary to
symbolically execute modern PHP systems. The observations regarding state state
explosion for method calls documented in Section \ref{} are only anecdotal and,
with the exception of \sf{WordPress}, we did not notice any significant impact
on scalability. Nevertheless, more research is required to better and
systematically understand possible drawbacks of object-oriented symbolic
execution. This question though is beyond the scope of this paper, as we aimed
to explore limitations of the practicality and scalability of static output
approximation using symbolic execution. Future work might address design
guidelines to enable programming analyzable applications, tool support to scale
the number of assumed symbolic inputs or systematically provide concrete data
to increase the practical benefit of the tools described above.

\section{Related Work} \label{sec:related_work}
\cite{Hills:2013:ESP:2483760.2483786}
\cite{wassermann2007sound,minamide2005static}
%\textcolor{blue}{\blindtext}
